Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-27 paper/ms.tex
updated the section on simulation and halo catalog

The Bolshoi simulation was performed in a cubic volume of 250 $h^{-1}$
Mpc on a side. It includes dark matter distribution is sampled using
$2048^{3}$ particles, which translates into a particle mass of $m_{\rm
  p}=1.35\times 10^{8}$ $h^{-1}$ M$_{\odot}$.  The cosmological
parameters are consistent with a WMAP5 and WMAP7 data with a matter
density $\Omega_{\rm m} = 0.27$, cosmological constant
$\Omega_{\Lambda}=0.73$, dimensionless Hubble constant $h=0.70$, slope
of the power spectrum $n=0.95$ and normalization of the power spectrum
$\sigma_{8}=0.82$ [REF].

We use halo catalogs constructed with a Friend-of-Friends (FOF)
algorithm with a linking lenght of 0.17 times the interparticle
distance. We have veryfied that the main results we present in this
paper also hold if instead we use halo catalogs constructed from a the
Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are
defined to have an density of 200 times the critical density. The
minimum halo mass in the models we construct in this \documentname correspond
to groups of $\sim 75$ particles. The catalogs were obtained from the
publicly available Multidark database \footnote{{\tt
    http://www.multidark.org/MultiDark/}}
\citep{2011arXiv1109.0003R}.

>>>>

The Bolshoi simulation \citep{Bolshoi} we use in this paper was
performed in a cubic volume of 250 $h^{-1}$ Mpc on a side. It includes
dark matter distribution is sampled using $2048^{3}$ particles, which
translates into a particle mass of $m_{\rm   p}=1.35\times 10^{8}$
$h^{-1}$ M$_{\odot}$.  The cosmological parameters are consistent with
a WMAP5 and WMAP7 data with a  density $\Omega_{\rm m} = 0.27$,
cosmological  $\Omega_{\Lambda}=0.73$, dimensionless Hubble constant
$h=0.70$, slope of the power spectrum $n=0.95$ and normalization of the
power spectrum$\sigma_{8}=0.82$ \citep{Komatsu2009,Jarosik2011}.

We use halo catalogs constructed with a Friend-of-Friends (FOF)
algorithm with a linking lenght of 0.17 times the interparticle
distance. 
%We have veryfied that the main results we present in this
%paper also hold if instead we use halo catalogs constructed from a the
%Bound Density Maxima (BDM) algorithm \citep{KlypinBDM} that are
%defined to have an density of 200 times the critical density. 
The minimum halo mass in the models we construct in this \documentname
correspond to groups of $\sim 75$ particles. The catalogs were
obtained from the publicly available Multidark database \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{2011arXiv1109.0003R}.
We focus our work on halos more massive than $1\times 10^{10}$\hMsun
that are resolved with at least $70$ particles.
